Pruning Subsequence Search with Attention-Based Embedding

### 2015-12-25 paper.tex
Make final camera-ready edits

An effective way to compare sequences is the dynamic time warping (DTW) distance, first proposed in the context of speech utterances \cite{sakoe1978dynamic}.
DTW first computes an optimal alignment of the two sequences of feature vectors being compared, and then reports their distance as the total distance between aligned feature vectors.
The alignment step makes DTW much more robust to timing and rate differences than more common metrics such as Euclidean distance \cite{rakthanmanon2012searching}.
DTW also naturally extends to the setting where subsequence matching is allowed.
Using dynamic programming, the optimal DTW alignment can be found in time quadratic in the length of the sequences, but even with this optimization, naive application of DTW to nearest-neighbor retrieval  can be prohibitively expensive.
Other dynamic programming-based ``edit distance'' metrics are used when appropriate, and are similar in both their effectiveness and expense.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{distances.pdf}
  \caption{Histograms of embedded distances for positive and negative example pairs in the validation set for our best-performing embedding network.  Note that the x-axis is log-scaled.}
  \label{fig:distances}
\end{figure}

>>>>

An effective way to compare sequences is the dynamic time warping (DTW) distance, first proposed in the context of speech utterances \cite{sakoe1978dynamic}.
DTW first computes an optimal alignment of the two sequences of feature vectors being compared, and then reports their distance as the total distance between aligned feature vectors.
The alignment step makes DTW much more robust to timing and rate differences than more common metrics such as Euclidean distance \cite{rakthanmanon2012searching}.
DTW also naturally extends to the setting where subsequence matching is allowed.
Using dynamic programming, the optimal DTW alignment can be found in time quadratic in the length of the sequences, but even with this optimization, naive application of DTW to nearest-neighbor retrieval  can be prohibitively expensive.
Other dynamic programming-based ``edit distance'' measures are used when appropriate, and are similar in both their effectiveness and expense.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{distances.pdf}
  \caption{Histograms of embedded distances for positive and negative example pairs in the validation set for our best-performing embedding network (c.f.\ \cite{raffel2015large} Figure 3).  Note that the x-axis is log-scaled.}
  \label{fig:distances}
\end{figure}
